Incentivizing Exploration by Heterogeneous Users

### 2018-02-15 algorithm.tex
addressed some comments

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than
$1/\log(s)$.
\bccomment{Do we need to mention what if $\frac{1}{\log(s)}>1$?}
\dkcomment{I'm not sure why. It's not like the inequality is not
  satisfied.}
Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/\log(s)$.
\pfedit{$1/\log(1)$ is treated as $\infty$, and if $1/\log(s) \ge 1$ then this condition is automatically met.}
\dkcomment{Do we need this?}
\end{itemize}

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time.
\dkcomment{I'm writing $n$ instead of $s$ here because $S_s$ would
  look ugly, and $n$ is consistent with the lemma.
  Or we could rename $S$ to something else.}
Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
\dkcomment{I'm not sure if we have defined the notation for components
  of vectors in the \emph{superscript}. Let's make sure not to forget it.}
renormalized to have standard deviation $1/2$.
\dkcomment{Is this the correct scaling.}
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
Specifically, we set $b(n) = \frac{n x^2}{16 \sigma^2}$,
and obtain that

@@

\dkcomment{The following paragraph is from Bangrui's version. It may
  move to an earlier section, go away, or become a part somewhere.}
As we can see later in our proof, we only need
$\max_{i,j}\limsup_{y\rightarrow 0^{+}}\frac{F_{i,j}(y)}{y}$ to be
finite.
Intuitively, Assumption~\ref{A1} states that there are not many agents
who are indifferent between their best arm and the second best arm.

@@

\bccomment{I believe the calculation up to this line should be correct now. The final equation we want to minimize is $\sum_{s=1}^{T}[\exp(-s*g^2(s))+g^2(s)*s]$, what should be our choice of $g(s)$?}

@@

on the cumulative expected regret.
\dkcomment{I see a problem here: What's the value of $x$ in the
  definition of \LatePhase? Presumably, we need to make $x$ small
  enough that any $x$ we use in any application of Lemma 7 (or
  Corollary 10) works. But notice that we use $x =
  \Theta(g^2(\tau_s^k))$,
  and in particular for the last step, I don't see how we can make
  $\tau_s^k$ much smaller than $T$.
  But then, we get that $x = O(\frac{\log T}{T})$, which would give
  linear regret. How to handle this?}
\end{proof}

>>>>

\begin{itemize}
\item $i$ has been pulled at most%
\footnote{in fact: exactly, since the algorithm entered phase $s$}
$s-1$ times up to time $t$, i.e., $\NumPull{t}{s} \leq s-1$.
\item Based on the current estimates \ArmEV{t}{i'} of all arms'
attribute vectors, the probability of pulling arm $i$ is less than
$1/\log(s)$. Let $\PullProb{t}{i} = \Prob[\AgV \sim \AgentDist]{\AgV \cdot \ArmEV{t}{i} > \AgV
  \cdot \ArmEV{t}{i'} \mbox{ for all } i' \neq i}$
be the probability that arm $i$ will be pulled
by the next (random) agent based on the current estimates. 
Then, the second criterion for payment-eligibility is that
$\PullProb{t}{i} < 1/\log(s)$.
\pfedit{$1/\log(1)$ is treated as $\infty$, and if $1/\log(s) \ge 1$ then this condition is automatically met.}
\dkcomment{Do we need this?}
\end{itemize}

@@

\begin{extraproof}{Lemma~\ref{lem:round-prob}}
Fix an arm $i$ and attribute $j$.
For any $n \geq 1$, let $k_n$ be the time step right after arm $i$ has
been pulled for the \Kth{n} time. Define
$S_n := \frac{n \cdot (\ArmE{k_n}{i}{j} - \Arm{i}{j})}{2 \sigma}$
to be the sum of all attribute-$j$ noise components up to and
including the \Kth{n} pull of arm $i$,
\dkcomment{I'm not sure if we have defined the notation for components
  of vectors in the \emph{superscript}. Let's make sure not to forget it.}
renormalized to have standard deviation $1/2$.
\dkcomment{Is this the correct scaling.}
The $S_n$ define an unbiased half-subgaussian random walk,
and we can therefore apply Lemma~\ref{lem:ACI-inequality} to them.
Specifically, we set $b(n) = \frac{n x^2}{16 \sigma^2}$,
and obtain that

@@

@@

@@

on the cumulative expected regret.

\bccomment{David, could you go through the proof again if possible? Thanks}

\end{proof}
